Misspecification Demonstration

### 2022-08-16 misspecification_study/misspec_demo.Rmd
apply Tim's fix for osa using model_q branch of wham

```{r comparecorrect}
correct_data_compare <- compare_wham_models(list(CD_em1 = em_fits[[1]][[1]],
                                                 CD_em2 = em_fits[[2]][[1]],
                                                 CD_em3 = em_fits[[3]][[1]],
                                                 CD_em4 = em_fits[[4]][[1]]))

print(correct_data_compare$g[[1]])
print(correct_data_compare$g[[2]])
```

@@

The catch and index four panel plots all look good for UR_em4. The problematic diagnostic is the NAA 4 panel plots, show below for ages 1 and 8 as well as the stacked barplot of residuals.

@@

>>>>

```{r comparecorrect}
# don't know why this code is not working anymore
# correct_data_compare <- compare_wham_models(list(CD_em1 = em_fits[[1]][[1]],
#                                                  CD_em2 = em_fits[[2]][[1]],
#                                                  CD_em3 = em_fits[[3]][[1]],
#                                                  CD_em4 = em_fits[[4]][[1]]))
# 
# print(correct_data_compare$g[[1]])
# print(correct_data_compare$g[[2]])
#        dAIC    AIC  rho_R rho_SSB rho_Fbar
# CD_em2  0.0 5008.4 0.2629 -0.0418   0.0573
# CD_em1  2.4 5010.8 0.3136 -0.0285   0.0416
# CD_em4  3.9 5012.3 0.2772 -0.0340   0.0506
# CD_em3  4.4 5012.8 0.3136 -0.0285   0.0416
# Error in if (is.na(rel.f.vals[x]) | any(diag(log.rel.ssb.rel.F.cov[[x]]) <  : 
#   missing value where TRUE/FALSE needed
```

@@

The catch and index four panel plots all look good for UR_em4. The problematic diagnostic is the NAA 4 panel plots, show below for ages 1 and 8 as well as the stacked barplot of residuals. Also, none of the one-step-ahead residual plots are currenlty working. Tim is looking into this, could be a non-trivial fix is required.

@@

![UR_em4 osa residuals for fleet](output/UR_em4/plots_png/diagnostics/Catch_age_comp_osa_resids_fleet_1.png)
